\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath,amsfonts}
\usepackage[colorlinks=true,linkcolor=blue,urlcolor=blue]{hyperref}
\usepackage{titlesec}

\titleformat{\section}{\large\bfseries}{\thesection}{1em}{}
\titleformat{\subsection}{\normalsize\bfseries}{\thesubsection}{1em}{}

\title{\textbf{Chronos Time v1.0:\\ Foundational Disclosure of a Universal Flow-Aligned Time System}}
\author{James Neil Elliott III}
\date{Original Development: January 2025\\Public Disclosure Timestamp: May 13, 2025}


\begin{document}

\maketitle

\begin{abstract}
Chronos Time is a flow-based, relativistically stable timekeeping model integrating quantum oscillation, gravitational influence, and dynamic energy structure. This document discloses the foundational equations underlying the Chronos system, without revealing applied technologies or implementation strategies. Public authorship is hereby timestamped and established.
\end{abstract}

\section*{Core Chronos Time Equations}

\subsection*{1. Quantum Frequency Definition}
\begin{equation}
C_T = \frac{1}{f_{\text{universal}}}
\end{equation}

\subsection*{2. General Relativistic Correction}
\begin{equation}
\Delta C_T' = \Delta C_T \sqrt{1 - \frac{v^2}{c^2} - \frac{2GM}{rc^2}}
\end{equation}

\subsection*{3. Quantum Time Unit Definition}
\begin{equation}
C_T,q = \frac{h}{mc^2}
\end{equation}

\subsection*{4. Flow-Based Time Progression}
\begin{equation}
\frac{dC_T}{d\tau} = \alpha F_L - \beta F_D
\end{equation}

\section*{Release Notice}

This document marks the minimal viable disclosure of Chronos Time.  
All implementation layers — including interfaces, integration, and systems of use — remain unpublished.

Further elaboration will proceed through sovereign channels, peer-reviewed extensions, or future flow-authorized disclosures.

\vspace{2em}
{\footnotesize \noindent License: Creative Commons Attribution-NonCommercial-NoDerivatives 4.0 (CC BY-NC-ND 4.0)}


\section*{References and Theoretical Foundations}
\begin{itemize} \item \textbf{General Relativity (Einstein, 1915)} – Time dilation through spacetime curvature is formalized in Equation (2). \Source: \url{https://doi.org/10.1007/BF01332580}
\item \textbf{Special Relativity (Einstein, 1905)} – Velocity-based time dilation is a partial basis of Equation (2). \Source: \url{https://www.fourmilab.ch/etexts/einstein/specrel/}
\item \textbf{Quantum Time Base (Planck’s Constant)} – Quantum time unit as described in Equation (3). \Source: \url{https://physics.nist.gov/cgi-bin/cuu/Value?h}
\item \textbf{Transcendent Flow Theory (Elliott, 2025)} – Energy flow structure and correction embedded in Equation (4). Also contributes to the geometry-coupled gravitational correction:

GitHub: \url{https://github.com/sl1ckj1mmy313/tft-may2025/releases} \ OSF: \url{https://osf.io/2je8h} \end{itemize}
\end{document}
